---
title: "Plotting ratio of green posting to low-carbon investment"
output: pdf_document
---

## ToDo

1. Setup
2. Plot raw ratio
3. Plot normalized ratio

## 1. Setup

```{r library, echo = F, message = F}
library(tidyverse)
library(here)
library(latex2exp)
```

```{r read_ratios}
ratios <- read_csv(here("data", "1_ratios.csv"))
glimpse(ratios)
```

## 2. Plot raw ratio

Let

$R = p \div i$ (Equation 1)

where $R$ is the raw ratio of green posting to low-carbon investment, $p$ is the 
green posting rate, and $i$ is the low-carbon investment share.

Further, let

$p = \frac{g}{(g + b)}$ (Equation 2)

where $g$ is the number of posts with any green label, and $b$ is the number of 
posts with any brown label *but* without a green label.

Further, let

$i = \frac{e}{c}$ (Equation 3)

where $e$ is the investment into low-carbon, and $c$ is capital expenditure 
(CapEx).

For now, omitting the year 2017 for which the total number of posts is very low
and the number of green posts is zero.

```{r raw}
ratios %>%
  filter(year != 2017) %>%
  ggplot(aes(x = year, y = posts_to_capex)) +
    geom_line() +
    labs(x = "Year", y = expression(paste("Ratio ",
                                          italic("R"))), 
         title = "Raw green posts to low-carbon investment ratio", 
         subtitle = "ExxonMobil, 2018–2024") +
    theme(
      plot.caption = element_text(hjust = 0)  # Left-align the caption
    )
```

## 3. Plot normalized ratio

Let 

$N = \frac{p - i}{p + i}$ (Equation 4)

where $N$ is the normalized ratio of green posting to low-carbon investment.

```{r normalized}
ratios %>%
  filter(year != 2017) %>%
  ggplot(aes(x = year, y = posts_to_capex_normalized)) +
    geom_line() +
    labs(x = "Year", y = expression(paste("Ratio ",
                                          italic("N"))), 
         title = "Normalized green posts to low-carbon investment ratio", 
         subtitle = "ExxonMobil, 2018–2024") +
    theme(
      plot.caption = element_text(hjust = 0)  # Left-align the caption
    )
```
